Automatic Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Handlebar Perturbations\\Version 4.dev

### 2025-11-13 main.tex
Started with imrpovement of introduction on types of falls and how we recreate them.

Riders fall when their control authority is not able to maintain a stable
vehicle state. There are many real world scenarios that can put the vehicle
into an uncontrollable state. External forces applied to the vehicle or rider
are one such scenario type and natural examples include wind gusts, handlebars
colliding with a neighbor's, a bag swinging from the handlebar, or simply
hitting a bump in the road. To assess our balance assisting bicycle, we subject
the rider to perturbations at the handlebar, which can easily cause a rider to
fall.

>>>>

Riders fall when their control authority is not able to maintain a stable
vehicle state. There are many real world scenarios that can put the vehicle
into an uncontrollable state. External forces applied to the vehicle or rider
are one such scenario type and natural examples include wind gusts, handlebars
colliding with a neighbor's, a bag swinging from the handlebar, or simply
hitting a bump in the road. To assess our balance assisting bicycle, we subject
the rider to perturbations at the handlebar, which can easily cause a rider to
fall. From a mechanics perspective, it is not particularly important how or
where the perturbation is applied but that it results in forcing the
bicycle-rider system into an unrecoverable state, as all forces acting on a
dynamical system can be resolved into an equivalent force and torque of a
couple at any location in the system~\citep{Kane1985}. We chose to perturb the
handlebar because of this principle and it was practical and required a low
force to cause a fall.
